---
title: "adc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{adc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)
```

```{r setup}
library(adc)
```

## Example 1: German Hyperinflation

In our first example, we will analyze the hyperinflation in Weimar Germany during the 1920's.  The data are monthly measurements of Germany's money supply and foreign exchange between 1921 and 1923.
```{r}
data("GermanHyperinflation")
plot(logM ~ log(pi), data = GermanHyperinflation)
```

Before the data can be analyzed, it must be put into the correct form with columns for `id`, `x` and `y`.  (`id` is set to 1 because there is one subject.)
```{r}
dat <- data.frame(id = 1,
                  x = log(GermanHyperinflation$pi),
                  y = GermanHyperinflation$logM)
```

Now the data can be analyzed with the internally studentized residuals at the 0.05 significance level, and no p-value adjustment.
```{r}
res <- adc(data = dat, eu = "in", pva = "none", alpha = 0.05)
```

We can examine the anomalie(s),
```{r}
table(res$ana)
res[res$ana, ]
```
Only the 29th observation is determined to be anomalous.  

The results can also be plotted to gain insight.
```{r}
res2 <- prepplot(res = res)
plot(y ~ x, data = res2, col = col, pch = pch)
```
The anomalous observation (red circle) lies far from the downward trend exhibited by the surrounding observations.  Furthermore, the replacement value (green triangle) is from the fitted curve.

## Example 2: More subjects

In this example, we will use the functions supplied with the package related to the simulation study.  Note that subjects 2 and 3 have anomalies of size 0 and 2 respectively, while subjects 1 and 4 have anomalies of size 1 (the default).  Therefore, subject 3 will have the largest anomaly, while subject 2 does not have an anomaly.
```{r}
set.seed(808)
dat1 <- rbind(create.data("Beta", 1),
              create.data("Cos" , 2, 0),
              create.data("Exp" , 3, 2),
              create.data("Quad", 4))
```

In the case of multiple subjects, we recommend plotting the results using **ggplot2** to take advantage of facetting by subject.
```{r,eval=requireNamespace("ggplot2")}
library(ggplot2)
ggplot(dat1, aes(x, y)) +
  geom_point() +
  theme_bw() +
  facet_wrap(~ id) +
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

We append some columns (`ana`, `rep` and `apv`), then analyze the four subjects sequentially with a `for` loop.  The defaults of `adc` are used corresponding with: the internally studentized residuals (`eu = "in"`), the Bejamini & Yekutieli procedure (`pva = "BY"`) and 0.01 level (`alpha = 0.01`).
```{r}
dat2 <- data.frame(id = dat1$id,
                   x = dat1$x,
                   y = dat1$y,
                   ana = NA,
                   rep = NA,
                   apv = NA)
uid <- unique(dat2$id)
for(i in 1:length(uid)) {
  rn <- dat2$id == uid[i]
  dat2_i <- dat2[rn, ]
  dat2[rn, ] <- adc(dat2_i)
}
table(dat2$ana)
dat2[dat2$ana, ]
```
As designed, anomalies were detected in subjects 1, 3 and 4; and subject 3 has the smallest adjusted p-value (`apv`), which corresponds with it being assigned the largest anomaly size.  Thus, only these subjects will be plotted according to their adjusted p-values.

```{r,eval=requireNamespace("ggplot2")}
dat3 <- prepplot(dat2)
ggplot(dat3, aes(x, y)) +
  geom_point(aes(shape = tpe2, colour = tpe2)) +
  scale_shape_manual(values = c(16, 16, 17)) +
  labs(colour = NULL, shape = NULL) +
  theme_bw() +
  theme(legend.position = "bottom") +
  facet_wrap(~ id2, nrow = 2) +
  scale_x_continuous(breaks = c(0, 0.5, 1))
```
