---
title: "Simple example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center"
)
```

```{r setup}
library(adc)
```

We will follow the example of Eubank (1985), and analyze Germany's hyperinflation in the 1920's.
```{r}
data("GermanHyperinflation")
plot(logM ~ log(pi), data = GermanHyperinflation)
```

Before we can analyze the data, we must put it into the correct form with columns for `id`, `x` and `y`.
```{r}
dat <- data.frame(id = 1,
                  x = log(GermanHyperinflation$pi),
                  y = GermanHyperinflation$logM)
```

Now we will analyze the data with the internally studentized residuals, without adjusing for mutiple comparisons, and at the $0.05$ significance level.
```{r}
res <- adc(data = dat, eu = "in", pva = "none", alpha = 0.05)
```

We can examine the anomalie(s),
```{r}
table(res$ana)
res[res$ana, ]
```
Our suspicions about the 19th observation are strengthened.

Plot.
```{r}
res2 <- prepplot(res = res)
plot(y ~ x, data = res2, col = col, pch = pch)
```
